A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-05-24 paper/paper1/ms.tex
Figures revised per CVM guidance
Revising figures per CVM

\begin{document}
\shorttitle{Runaway Mass Loss in HAT-P-67b}
\shortauthors{TBD}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
    \caption{Overlay of all 128 individual HPF exposures of HAT-P-67, spanning 2020-2022. Variability is seen in the \ion{He}{1} 10833 \AA~ triplet, denoted by the vertical orange shaded band, but not in the adjacent regions.  These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.  Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 \AA.}
    \label{fig:HPFheliumOverview}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=5cm]{figures/centroid_overview10833.png} }
    \hskip-3em
    \subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
    \caption{Line centroid positions of the  \ion{He}{1} 10830 \AA~ feature.  \emph{left}: The overview panel shows a slight blueshift relative to the stellar restframe, and a weak excess blueshift trend after planet egress. \emph{right:} The detailed zoom-in of the in-transit phase shows a redshift relative to the planet restframe at ingress and a blueshift relative to the planet restframe near egress.  The line-of-sight velocity distribution of 2-3 \AA~ means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
    \label{fig:centroids}
\end{figure}

>>>>

\begin{document}
\shorttitle{Runaway Mass Loss in HAT-P-67b}
\shortauthors{Gully-Santiago et al.}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
    \caption{Overlay of all 152 individual HPF exposures of HAT-P-67, spanning 2020-2022. Variability is seen in the \ion{He}{1} 10833 \AA~ triplet, denoted by the vertical orange shaded band, but not in the adjacent regions.  These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.  Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 \AA.}
    \label{fig:HPFheliumOverview}
\end{figure}

Figure \ref{fig:HPFperCampaign} shows the spectra for four campaigns, with before and after spectra showing conspicuous excess absorption during transit and 1 day before transit, but negligible excess absorption after transit.  The individual transits show significant morphological variation, with substructure in the bulk line-of-sight velocity distribution.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT_P_67b_byCampaign_Spectra.png}
    \caption{Four observing campaigns centered on an in-transit epoch with before-and-after visits typically separated by 1 night. The after-transit spectra tend to show negligible absorption.  Line-of-sight velocity substructure can be seen in the before and during transit epochs.}
    \label{fig:HPFperCampaign}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/centroid_overview10833.png}
    %\hskip-3em
    %\subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
    \caption{Line centroid positions of the  \ion{He}{1} 10830 \AA~ feature.  A slight blueshift relative to the stellar restframe (vertical line) can be seen, with a weak excess blueshift trend after planet egress. The line-of-sight velocity distribution of 2-3 \AA~ means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
    \label{fig:centroids}
\end{figure}
